---
title: "IM3 Run Analysis"
author: "Created by: `r Sys.info()['user']`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document: 
    css: custom.css
    toc: yes
---

```{r setOptions, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set up default options for chunks, turn off error or warning messages.
knitr::opts_chunk$set(echo=FALSE, comment=NA, warning=FALSE, message=FALSE, include=TRUE,
                      fig.path='//nrelqnap02/plexos/projects/im3/run results/plots/', dev='png', fig.width=18)

library(data.table)
library(ggplot2)
library(plyr)
library(knitr)
library(rplexos)

fig.height.gen.types = 8
fig.height.reserves = 8
fig.height.duration = 8
element.text.size = 12

plot.theme = theme_bw() + 
  theme(axis.text.x = element_text(angle = -30, hjust=0, size=element.text.size),
        axis.title = element_text(size = 16),
        axis.text.y = element_text(size = 15),
        strip.text.x = element_text(size = 20),
        strip.text.y = element_text(size = 20),
        legend.text = element_text(size = 20) ) 
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Total Generation Cost with Penalties
```{r total-gen-cost-penalties}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = annual.gen.stats) +
  geom_col(aes(x=Scenario, y=`Total Cost ($)`, colour='gray25'), show.legend=FALSE) +
  # scale_fill_manual('', values = fuel.color) +
  ylab('Generation Cost ($)') + xlab('Scenario') +
  plot.theme

# ggplot(data = annual.gen.stats) +
#   geom_col(aes(x=Scenario, y=`Total Cost ($)`, fill=Scenario, colour='black'), show.legend=FALSE) +
#   # scale_fill_manual('', values = fuel.color) +
#   ylab('Generation Cost ($)') + xlab('Scenario') +
#   plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Total Generation Cost without Penalties
```{r total-gen-cost}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = annual.gen.stats) +
  geom_col(aes(x=Scenario, y=`Cost ($)`, colour='gray25'), show.legend=FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  ylab('Generation Cost ($)') + xlab('Scenario') +
  plot.theme

# ggplot(data = annual.gen.stats) +
#   geom_col(aes(x=Scenario, y=`Cost ($)`, fill=Scenario, colour='black'), show.legend=FALSE) +
#   # scale_fill_manual('', values = fuel.color) +
#   ylab('Generation Cost ($)') + xlab('Scenario') +
#   plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


***
## Average Region Energy Price
```{r energy-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
avg.prices$Scenario = factor(avg.prices$Scenario, levels = plotting.order)

ggplot(data = avg.prices) +
  geom_col(aes(x=Scenario, y=`Price  ($/MWh)`, color='gray25'), show.legend=FALSE) +
  xlab('Scenario') + ylab('Avg Energy Price ($/MWh)') +
  # scale_fill_manual('', values = scenario.color) +
  plot.theme

# ggplot(data = avg.prices) +
#   geom_col(aes(x=Scenario, y=`Price  ($/MWh)`, fill=Scenario, colour='black'), show.legend=FALSE) +
#   xlab('Scenario') + ylab('Avg Energy Price ($/MWh)') +
#   # scale_fill_manual('', values = fuel.color) +
#   plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Average Zone Energy Price
```{r zone-energy-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
avg.zone.price$Scenario = factor(avg.zone.price$Scenario, levels = plotting.order)

ggplot(data = avg.zone.price) +
  geom_col(aes(x=Scenario, y=`Price  ($/MWh)`, color='gray25'), show.legend=FALSE) +
  xlab('Scenario') + ylab('Avg Energy Price ($/MWh)') +
  # scale_fill_manual('', values = scenario.color) +
  plot.theme

# ggplot(data = avg.zone.price) +
#   geom_col(aes(x=Scenario, y=`Price  ($/MWh)`, fill=Scenario, colour='black'), show.legend=FALSE) +
#   xlab('Scenario') + ylab('Avg Energy Price ($/MWh)') +
#   # scale_fill_manual('', values = fuel.color) +
#   plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Hours with High Price
```{r high-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
hours.high.price$Scenario = factor(hours.high.price$Scenario, levels = plotting.order)

ggplot(data = hours.high.price) +
  geom_col(aes(x=Scenario, y=`# Hours over 100 $/MWh`, color='gray25'), show.legend=FALSE) +
  xlab('Scenario') + ylab('Hours with High Price') +
  # scale_fill_manual('', values = scenario.color) +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Unserved Energy
```{r violations-energy}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
violations$Scenario = factor(violations$Scenario, levels = plotting.order)

ggplot(data = violations) +
  geom_col(aes(x=Scenario, y=`Unserved Energy (MWh)`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Unserved Energy (MWh)') +
  plot.theme

ggplot(data = violations) +
  geom_col(aes(x=Scenario, y=`Hours with Unserved Energy`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hours with Unserved Energy') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Line Flow Violation
```{r violations-line-flow}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

ggplot(data = violations) +
  geom_col(aes(x=Scenario, y=`Line Flow Violation (MWh)`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Line Flow Violation (MWh)') +
  plot.theme

ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Hours with Line Flow Violation`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hours with Line Flow Violation') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Reserve Shortage
```{r violations-reserve}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Reserve Shortage (MWh)`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Reserve Shortage (MWh)') +
  plot.theme

ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Hours with reserve shortage`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hours with reserve shortage') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Hydro Violation
```{r violations-hydro}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Hydro Energy Violation (kWh)`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hydro Energy Violation (kWh)') +
  plot.theme

ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Hours with Hydro Violation`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hours with Hydro Violation') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Line Congestion
```{r line-congestion}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = annual.gen.stats) + geom_col(aes(x=Scenario, y=`# Congested Lines`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('# of Congested Lines') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Penalty Costs
```{r penalty-costs}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
penalty$Scenario = factor(penalty$Scenario, levels = plotting.order)

ggplot(data = penalty) + geom_bar(aes(x=Scenario, y=cost, fill=violation), position='stack', stat='identity') +
  xlab('Scenario') + ylab('Penalty Cost ($)') +
  plot.theme +
  guides(fill=guide_legend(title='Type'))
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Coal and Natural Gas Offtake
```{r fuel-offtake}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = fuel.offtake) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  xlab('Scenario') + ylab('Fuel Offtake (GBtu)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Total Curtailment
```{r total-curtailment}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = annual.gen.stats) + geom_col(aes(x=Scenario, y=`Curtailment (GWh)`, color='gray25'), show.legend = FALSE) +
  ylab('Curtailment GWh') + scale_fill_manual('', values = scenario.color) + xlab('Scenario') +
  plot.theme

ggplot(data = annual.gen.stats) + geom_col(aes(x=Scenario, y=`Curtailment %`, color='gray25'), show.legend = FALSE) +
  xlab('Scenario') + ylab('Curtailment %') + scale_fill_manual('', values = scenario.color) +
  plot.theme

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Generation Percent by Type
```{r generation-percent, fig.height=fig.height.gen.types}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = gen.by.type) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Gen (% of load)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Generation by Type and Region
```{r generation-type-region, fig.height=fig.height.gen.types*3, fig.width=18}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = gen.type.region) + geom_bar(aes(x=Scenario, y=value, fill=Type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Gen (GWh)') +
  facet_grid(TEPPC.Region~., scales='free_y') +
  plot.theme

# # This code was used for the AGU presentation plots I made
# gen.type.region$TEPPC.Region = factor(gen.type.region$TEPPC.Region, levels = c('Basin', 'Southern California', 'Southwest', 'Northwest', 'Canada',
#                                                                                'Northern California', 'Rockies', 'Mexico'))
# ggplot(data = gen.type.region[TEPPC.Region %in% c('Basin', 'Southern California', 'Southwest', 'Northwest'),]) + geom_bar(aes(x=Scenario, y=value, fill=Type), position='stack', stat='identity') +
#   scale_fill_manual('', values = gen.color) +
#   xlab('Scenario') +
#   ylab('Gen (GWh)') +
#   facet_grid(TEPPC.Region~., scales='free_y') +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = -30, hjust=0, size=16),
#         axis.title = element_text(size = 20),
#         axis.text.y = element_text(size = 20),
#         strip.text.x = element_text(size = 20),
#         strip.text.y = element_text(size = 20),
#         legend.text = element_text(size = 18) )
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Capacity Factor
```{r capacity-factor, fig.height=fig.height.gen.types}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = capacity.factor) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Capacity Factor (%)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## % Reserves of Reserves+Generation
```{r reserve-percent, fig.height=fig.height.gen.types}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = reserve.generation.percent) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('% Reserve of Reserve+Gen') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Reserve Provision by Type
```{r reserve-provision, fig.height=fig.height.gen.types}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = reserve.provision) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Reserve Provison (GWh)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Reserve Provision by Type and Region
```{r reserve-provision-region, fig.height=fig.height.gen.types*8}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = reserve.provision.region) + geom_bar(aes(x=Scenario, y=value, fill=Type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Reserve Provison (GWh)') +
  facet_grid(TEPPC.Region~., scales='free_y') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Imports and Exports by Region
```{r imports-exports-region, fig.height=fig.height.gen.types*8}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = imports.exports) +
  # geom_bar(aes(x=Scenario, y=Net.Exports, colour='black'), position='dodge', stat='identity') +
  geom_col(aes(x=Scenario, y=Net.Exports, colour='black'), show.legend=FALSE) +
  # scale_fill_manual('', values = fuel.color) +
  # scale_fill_manual('', values = gen.color) +
  xlab('Imports/Exports') +
  ylab('Net Exports (GWh)') +
  facet_grid(TEPPC.Region~., scales='free_y') +
  plot.theme


# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


***
## Energy Price Duration Curve
```{r energy-price-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = prices[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=Cost, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('Energy Price ($/MWh)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Coal Gens not at Max Cap Duration Curve
```{r coal-operation-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = coal.gen[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=value, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('Coal Gens not at Max Cap') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Reserve Shortage Duration Curve
```{r reserve-shortage-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = reserve.shortage[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=value, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('Reserve Shortages') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## TX Congestion Duration Curve
```{r tx-congestion-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = tx.congestion[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=value, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('TX Congestion') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## TX Violation Duration Curve
```{r tx-violation-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = tx.violations[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=value, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('TX Violation') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Violations
```{r violations-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(violations)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Annual Stats
```{r annual-stats-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(annual.gen.stats)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Average Region Electricity Price
```{r average-electricity-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(avg.prices)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Average Zone Electricity Price
```{r average-zone-electricity-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(avg.zone.price)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Hours with price > 100 $/MWh
```{r hours-high-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(hours.high.price)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Percent Generation by Type
```{r gen-type-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(gen.type.percent)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Capacity Factor
```{r capacity-factor-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(cap.factor)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Percent Reserve of Reserve+Generation
```{r percent-reserve-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(reserve.gen.percent)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Reserve Provision by Type
```{r reserve-provision-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(reserve.type)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```







