---
title: "IM3 Run Analysis"
author: "Created by: `r Sys.info()['user']`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document: 
    css: custom.css
    toc: yes
---

```{r setOptions, echo=FALSE, warning=FALSE, message=FALSE, error=FALSE}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set up default options for chunks (sections), turn off error or warning messages.
knitr::opts_chunk$set(echo=FALSE, comment=NA, warning=FALSE, message=FALSE, include=TRUE,
                      fig.path='//nrelqnap02/plexos/projects/im3/run results/plots/', dev='png', fig.width=18)

# Load required R libraries
library(data.table)
library(ggplot2)
library(plyr)
library(knitr)
library(rplexos)

# Set figure height and text size options
fig.height.gen.types = 8
fig.height.reserves = 8
fig.height.duration = 8
element.text.size = 12

# Create plot theme to use for generic plot template
plot.theme = theme_bw() + 
  theme(axis.text.x = element_text(angle = -30, hjust=0, size=element.text.size),
        axis.title = element_text(size = 16),
        axis.text.y = element_text(size = 15),
        strip.text.x = element_text(size = 20),
        strip.text.y = element_text(size = 20),
        legend.text = element_text(size = 20) ) 
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Total Generation Cost with Penalties
```{r total-gen-cost-penalties}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Create plot of total generation cost, which includes all penalties during the plexos simulation
ggplot(data = annual.gen.stats) +
  geom_col(aes(x=Scenario, y=`Total Cost ($)`, fill=Scenario, colour='black'), show.legend=FALSE) +
  scale_fill_manual('', values = fuel.color) +
  ylab('Generation Cost ($)') + xlab('Scenario') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Total Generation Cost without Penalties
```{r total-gen-cost}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Create plot of total generation for each scenario, ignoring any penalty costs during the plexos simulation.
ggplot(data = annual.gen.stats) +
  geom_col(aes(x=Scenario, y=`Cost ($)`/1000000000, fill=Scenario, colour='black'), show.legend=FALSE) +
  
   geom_errorbar(aes(x = Scenario, ymin=min(annual.gen.stats[grep('1993', Scenario), .(`Cost ($)`)])/1000000000, 
                                   ymax=min(annual.gen.stats[grep('1993', Scenario), .(`Cost ($)`)])/1000000000),
                            size=0.65, linetype='dashed', color='black') +
   geom_errorbar(aes(x = Scenario, ymin=max(annual.gen.stats[grep('1993', Scenario), .(`Cost ($)`)])/1000000000, 
                                   ymax=max(annual.gen.stats[grep('1993', Scenario), .(`Cost ($)`)])/1000000000),
                          size=0.65, linetype='dashed', color='black') +
  
  scale_fill_manual('', values = fuel.color) +
  ylab('Generation Cost (Billion $)') + xlab('Scenario') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


***
## Average Region Energy Price
```{r energy-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set scenarios as factors so they are in the correct order in the plots.
avg.prices.regions$Scenario = factor(avg.prices.regions$Scenario, levels = plotting.order)

# Create plot of average regional energy price for all regions and all periods
ggplot(data = avg.prices.regions) +
  geom_col(aes(x=Scenario, y=`Price  ($/MWh)`, fill=Scenario, colour='black'), show.legend=FALSE) +
  xlab('Scenario') + ylab('Avg Energy Price ($/MWh)') +
  scale_fill_manual('', values = fuel.color) +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Average Zone Energy Price
```{r zone-energy-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set scenarios as factors so they are in the correct order in the plots.
avg.prices.zones$Scenario = factor(avg.prices.zones$Scenario, levels = plotting.order)

# Create plot of average zone energy price for all zones and all periods
ggplot(data = avg.prices.zones) +
  geom_col(aes(x=Scenario, y=`Price  ($/MWh)`, fill=Scenario, colour='black'), show.legend=FALSE) +
  xlab('Scenario') + ylab('Avg Energy Price ($/MWh)') +
  scale_fill_manual('', values = fuel.color) +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Average BA Energy Price
```{r ba-energy-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# List of all regions in region.price object
region.names = unique(region.price$region)

# Create plot of average annual energy price for each BA (plexos region in the database)
for ( i in region.names) {
  p = ggplot(data = region.price[region==i,]) +
    geom_col(aes(x=Scenario, y=value, fill=Scenario, colour='black'), show.legend=FALSE) +
    xlab('Scenario') + ylab('Avg BA Energy Price ($/MWh)') +
    scale_fill_manual('', values = fuel.color) +
    plot.theme
  print(i)
  print(p)
}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Average TEPPC Region Energy Price
```{r teppc-energy-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# List all TEPPC regions
region.names = unique(region.price.teppc$TEPPC.Region)

# Create a plot of average annual TEPPC region energy price, for each TEPPC region
for ( i in region.names) {
  p = ggplot(data = region.price.teppc[TEPPC.Region==i,]) +
    geom_col(aes(x=Scenario, y=value, fill=Scenario, colour='black'), show.legend=FALSE) +
    xlab('Scenario') + ylab('Avg BA Energy Price ($/MWh)') +
    scale_fill_manual('', values = fuel.color) +
    plot.theme 
  print(i)
  print(p)
}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Hours with High Price
```{r high-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set scenarios as factors for plotting
hours.high.price$Scenario = factor(hours.high.price$Scenario, levels = plotting.order)

# Create plot of number of hours with energy prices over 100 $/MWh for each scenario
ggplot(data = hours.high.price) +
  geom_col(aes(x=Scenario, y=`# Hours over 100 $/MWh`, color='gray25'), show.legend=FALSE) +
  xlab('Scenario') + ylab('Hours with High Price') +
  # scale_fill_manual('', values = scenario.color) +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Unserved Energy
```{r violations-energy}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Set scenarios as factors for plotting
violations$Scenario = factor(violations$Scenario, levels = plotting.order)

# Create plot of unserved energy for each scenario
ggplot(data = violations) +
  geom_col(aes(x=Scenario, y=`Unserved Energy (MWh)`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Unserved Energy (MWh)') +
  plot.theme

# Create plot of # of hours with unserved energy for each scenario
ggplot(data = violations) +
  geom_col(aes(x=Scenario, y=`Hours with Unserved Energy`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hours with Unserved Energy') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Line Flow Violation
```{r violations-line-flow}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Create plot of line flow violation for each scenario, in MWh
ggplot(data = violations) +
  geom_col(aes(x=Scenario, y=`Line Flow Violation (MWh)`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Line Flow Violation (MWh)') +
  plot.theme

# Create plot of # of hours of line flow violation for each scenario
ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Hours with Line Flow Violation`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hours with Line Flow Violation') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Reserve Shortage
```{r violations-reserve}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# Plot of reserve shortage
ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Reserve Shortage (MWh)`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Reserve Shortage (MWh)') +
  plot.theme

# Plot of # of hours of reserve shortage
ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Hours with reserve shortage`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hours with reserve shortage') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Hydro Violation
```{r violations-hydro}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Hydro Energy Violation (kWh)`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hydro Energy Violation (kWh)') +
  plot.theme

ggplot(data = violations) + geom_col(aes(x=Scenario, y=`Hours with Hydro Violation`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('Hours with Hydro Violation') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Line Congestion
```{r line-congestion}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = annual.gen.stats) + geom_col(aes(x=Scenario, y=`# Congested Lines`, color='gray25'), show.legend = FALSE) +
  # scale_fill_manual('', values = scenario.color) +
  xlab('Scenario') + ylab('# of Congested Lines') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Penalty Costs
```{r penalty-costs}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
penalty$Scenario = factor(penalty$Scenario, levels = plotting.order)

ggplot(data = penalty) + geom_bar(aes(x=Scenario, y=cost, fill=violation), position='stack', stat='identity') +
  xlab('Scenario') + ylab('Penalty Cost ($)') +
  plot.theme +
  guides(fill=guide_legend(title='Type'))
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Coal and Natural Gas Offtake
```{r fuel-offtake}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = fuel.offtake) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  xlab('Scenario') + ylab('Fuel Offtake (GBtu)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Total Curtailment
```{r total-curtailment}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = annual.gen.stats) + geom_col(aes(x=Scenario, y=`Curtailment (GWh)`, color='gray25'), show.legend = FALSE) +
  ylab('Curtailment GWh') + scale_fill_manual('', values = scenario.color) + xlab('Scenario') +
  plot.theme

ggplot(data = annual.gen.stats) + geom_col(aes(x=Scenario, y=`Curtailment %`, color='gray25'), show.legend = FALSE) +
  xlab('Scenario') + ylab('Curtailment %') + scale_fill_manual('', values = scenario.color) +
  plot.theme

# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Generation Percent by Type
```{r generation-percent, fig.height=fig.height.gen.types}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
# ggplot(data = gen.by.type) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
#   scale_fill_manual('', values = gen.color) +
#   xlab('Scenario') +
#   ylab('Gen (% of load)') +
#   plot.theme

other.gen.types = gen.by.type[!type %in% c('Hydro', 'Coal', 'Natural Gas'), .(type = 'Other', value = sum(value)), by=Scenario]
# other.gen.types$type = factor(other.gen.types$type, levels = plotting.order)
plot.data = rbind(gen.by.type[!type %in% c('Other')], other.gen.types)

ggplot(data = plot.data[type %in% c('Other', 'Hydro', 'Coal', 'Natural Gas')  , ]) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Gen (% of load)') +
  plot.theme +
  theme(legend.text = element_text(size=10))
        # ,
        # legend.background = element_rect(size = 0.5, color='black'))
        # ,
        # legend.position = c(0.9,0.26))
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Generation by Type and Region
```{r generation-type-region, fig.height=fig.height.gen.types*3, fig.width=18}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
gen.type.region[ TEPPC.Region == 'Desert SouthWest', TEPPC.Region := 'Desert Southwest']
annual.load[ TEPPC.Region == 'Southwest', TEPPC.Region := 'Desert Southwest']

other.gen.types = gen.type.region[!Type %in% c('Hydro', 'Coal', 'Natural Gas'), .(Type = 'Other', value = sum(value)), by=.(Scenario, TEPPC.Region)]
plot.data = rbind(gen.type.region, other.gen.types)

ggplot(data = plot.data[!TEPPC.Region %in% c('Canada', 'Mexico') & Type %in% c('Other', 'Hydro', 'Coal', 'Natural Gas'),]) +
  geom_bar(aes(x=Scenario, y=value/1000, fill=Type), position='stack', stat='identity') +
  geom_errorbar(data = annual.load[!TEPPC.Region %in% c('Canada', 'Mexico')], aes(x = Scenario, ymin=value/1000, ymax=value/1000, color='grey20'),
                            size=0.65, linetype='longdash') +
  scale_fill_manual('', values = gen.color) +
  scale_color_manual('', values = c('grey20'), labels=c('Load'))+
  xlab('Scenario') +
  ylab('Generation (TWh)') +
  facet_grid(TEPPC.Region~.) +
  plot.theme                                                                                                    
                                                                                                    
# ggplot(data = gen.type.region[!TEPPC.Region %in% c('Canada', 'Mexico'),]) +
#   geom_bar(aes(x=Scenario, y=value, fill=Type), position='stack', stat='identity') +
#   geom_errorbar(data = annual.load[!TEPPC.Region %in% c('Canada', 'Mexico')], aes(x = Scenario, ymin=value, ymax=value, color='grey20'),
#                             size=0.65, linetype='longdash') +
#   scale_fill_manual('', values = gen.color) +
#   scale_color_manual('', values = c('grey20'), labels=c('Load'))+
#   xlab('Scenario') +
#   ylab('Gen (GWh)') +
#   facet_grid(TEPPC.Region~.) +
#   plot.theme

# # This code was used for the AGU presentation plots I made
# gen.type.region$TEPPC.Region = factor(gen.type.region$TEPPC.Region, levels = c('Basin', 'Southern California', 'Southwest', 'Northwest', 'Canada',
#                                                                                'Northern California', 'Rockies', 'Mexico'))
# ggplot(data = gen.type.region[TEPPC.Region %in% c('Basin', 'Southern California', 'Southwest', 'Northwest'),]) + geom_bar(aes(x=Scenario, y=value, fill=Type), position='stack', stat='identity') +
#   scale_fill_manual('', values = gen.color) +
#   xlab('Scenario') +
#   ylab('Gen (GWh)') +
#   facet_grid(TEPPC.Region~., scales='free_y') +
#   theme_bw() +
#   theme(axis.text.x = element_text(angle = -30, hjust=0, size=16),
#         axis.title = element_text(size = 20),
#         axis.text.y = element_text(size = 20),
#         strip.text.x = element_text(size = 20),
#         strip.text.y = element_text(size = 20),
#         legend.text = element_text(size = 18) )
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Capacity Factor
```{r capacity-factor, fig.height=fig.height.gen.types}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = capacity.factor) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Capacity Factor (%)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## % Reserves of Reserves+Generation
```{r reserve-percent, fig.height=fig.height.gen.types}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = reserve.generation.percent) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('% Reserve of Reserve+Gen') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Reserve Provision by Type
```{r reserve-provision, fig.height=fig.height.gen.types}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = reserve.provision) + geom_bar(aes(x=Scenario, y=value, fill=type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Reserve Provison (GWh)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Reserve Provision by Type and Region
```{r reserve-provision-region, fig.height=fig.height.gen.types*8}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = reserve.provision.region) + geom_bar(aes(x=Scenario, y=value, fill=Type), position='stack', stat='identity') +
  scale_fill_manual('', values = gen.color) +
  xlab('Scenario') +
  ylab('Reserve Provison (GWh)') +
  facet_grid(TEPPC.Region~., scales='free_y') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```

***
## Imports and Exports by Region
```{r imports-exports-region, fig.height=fig.height.gen.types*8}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = imports.exports) +
  # geom_bar(aes(x=Scenario, y=Net.Exports, colour='black'), position='dodge', stat='identity') +
  geom_col(aes(x=Scenario, y=Net.Exports, fill=Scenario, colour='black'), show.legend=FALSE) +
  scale_fill_manual('', values = fuel.color) +
  # scale_fill_manual('', values = gen.color) +
  xlab('Imports/Exports') +
  ylab('Net Exports (GWh)') +
  facet_grid(TEPPC.Region~., scales='free_y') +
  plot.theme


# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
```


***
## Energy Price Duration Curve
```{r energy-price-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = prices[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=Cost, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('Energy Price ($/MWh)') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Coal Gens not at Max Cap Duration Curve
```{r coal-operation-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = coal.gen[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=value, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('Coal Gens not at Max Cap') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Reserve Shortage Duration Curve
```{r reserve-shortage-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = reserve.shortage[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=value, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('Reserve Shortages') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## TX Congestion Duration Curve
```{r tx-congestion-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = tx.congestion[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=value, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('TX Congestion') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## TX Violation Duration Curve
```{r tx-violation-duration, fig.height=fig.height.duration}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
ggplot(data = tx.violations[Scenario %in% scenarios, ]) +
  geom_line(aes(x=interval, y=value, color = Scenario), size=1) +
  scale_y_continuous(limits = c(0, 300)) +
  scale_color_manual('', values = scenario.color) +
  xlab('Hours of Year') + ylab('TX Violation') +
  plot.theme
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Violations
```{r violations-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(violations)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Annual Stats
```{r annual-stats-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(annual.gen.stats)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Average Region Electricity Price
```{r average-electricity-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(avg.prices.regions)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Average Zone Electricity Price
```{r average-zone-electricity-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(avg.prices.zones)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Hours with price > 100 $/MWh
```{r hours-high-price}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(hours.high.price)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Percent Generation by Type
```{r gen-type-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(gen.type.percent)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Capacity Factor
```{r capacity-factor-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(cap.factor)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Percent Reserve of Reserve+Generation
```{r percent-reserve-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(reserve.gen.percent)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```

***
## Reserve Provision by Type
```{r reserve-provision-table}
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
kable(reserve.type)
# %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% -->
```







